Think deep for reef resilience

### 2025-08-10 paper/paper_draft.qmd
Remove unnecessary detail

The five selected GCMs span a range of Equilibrium Climate Sensitivity (ECS) values within
the Intergovernmental Panel on Climate Change (IPCC) assessed likely range, and a range of
GCM development families \[**TI: Ben, what does "GCM development families" mean?**\]. The
IPCC defines ECS as the long term warming caused by a doubling of carbon dioxide above its
pre-industrial concentration [@forster2021]. The five GCMs therefore allow for a range of
possible climate futures to be explored, capturing the uncertainty in future responses to
CO2 increases (@sfig-ecs; @fig-methods-dhws; [@grose2023; @shepherd2018]). Projections using
Shared Socio-economic Pathway (SSP) 2-4.5 was used to represent the plausible emission
pathway. It represents a moderate emissions scenario with continued CO2 emissions comparable
to present day until 2050, after which emissions gradually decline. Under this scenario,
atmospheric concentrations approximately reach 540ppm by 2100 [@hausfather2020; IPCC
-@climate2023]. The selected GCMs represent 2.5°C to 4.31°C of global atmospheric warming in
the 2081-2100 period relative to 1850-1900.

>>>>

The five selected GCMs span a range of Equilibrium Climate Sensitivity (ECS) values within
the Intergovernmental Panel on Climate Change (IPCC) assessed likely range, and a range of
GCM development families \[**TI: Ben, what does "GCM development families" mean?**\]. The
IPCC defines ECS as the long term warming caused by a doubling of carbon dioxide above its
pre-industrial concentration [@forster2021]. The five GCMs therefore allow for a range of
possible climate futures to be explored, capturing the uncertainty in future responses to
CO2 increases (@sfig-ecs; @fig-methods-dhws; [@grose2023; @shepherd2018]). Projections using
Shared Socio-economic Pathway (SSP) 2-4.5 was used to represent the plausible emission
pathway. It represents a moderate emissions scenario with continued CO2 emissions comparable
to present day until 2050, after which emissions gradually decline [@hausfather2020; IPCC
-@climate2023]. The selected GCMs represent 2.5°C to 4.31°C of global atmospheric warming in
the 2081-2100 period relative to 1850-1900.
